---
title: "HW-Week3"
author: "Zhuoyang Chen"
date: "January 22, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions
##1. A somatic human cell contains about 6 picograms of DNA. How much DNA does a sperm cell contain?
3 picogram. A sperm is a progenitor of human (halpoid) so just contains half of the chromosomes (6/2 pg).

##2. How many human cells with you need to obtain 10 micrograms of DNA, as is requested by many sequencing protocols?
1666667. As in question 1 saying that a human somatic cell contain 6 picograms of DNA, we have to provide 10e6 / 6 = 1666666.7 cells.

##3. Describe one typical cause for DNA loss during DNA extraction.
That could be DNA still remains on the solid absorber whthin the column after buffer washing.

##4. Describe two functions of the adapters that are typically added during Illumina's library preparations. Which types of sequences do they often entails?
1. Necessary for template DNA to be immobilized on the lane whthin a sequencer and then initializes the first round of sequencing (a pcr step before bridge pcr).

2. Necessary for the newly synthesized complemetary DNA to fold over into a bridge-like shape to initialize bridge pcr.

They often have a) P5 and P7, which are necessary for template DNA to bind and initializing bridge pcr, b) adapter trimming sequence, which would be used to ensure unidirection sequencing, and convenient for data preprocessing and quality control, c) indices and primers for indices, and d) primers for insertional DNA sequencing.

## 5. Components of what kind of lab equipment have to be integrated in any type of Illumina sequencer?

#Exercises
##1. Write a for-loop to download all fastq files of WT biological replicate NO. 2 of the Gierlinski data set. Try to have a solution as generally applicable as possible.

##2. Why are there multiple fastq files per sample? What does each file represent?

##3. Count the number of reads stored in each FASTQ file and keep a note of the results. The zcat command allows you to see the contents of a gzipped file.

#Project
##1. Identify and write down one or two biological or technical questions of interest for your project.
```{r}
```

custom output in r like `r x`

